---
title: "Project1"
author: "Sam Reeves"
date: "2/28/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Chess Tournament Cross-Table Analysis 

Given a .txt file with the results and player statistics of a single small tournament, output a .csv with some more information.

--------------------------------------------------------------------

### Load libraries and Data

```{r}
library(stringr)
url <- "https://raw.githubusercontent.com/TheWerefriend/data607/master/project1/tournamentinfo.txt"
text <- read.delim(url, skip = 3)
```


### Data Extraction

Create basic vectors:

  1. Player Name
  2. State
  3. Points
  2. PreRating
  3. PostRating
  4. List of Opponents

```{r}
name <- c()
state <- c()
points <- c()
preR <- c()
postR <- c()
opp <- c()

for (line in text) {
  name <- c(name, str_extract(line, "[A-Z][A-Z]+ [A-Z ]+"))
  state <- c(state, str_extract(line, " [A-Z]{2} \\|"))
  points <- c(points, str_extract(line, "\\d\\.\\d"))
  preR <- c(preR, str_extract(line, "R: +\\d{3,4}"))
  postR <- c(postR, str_extract(line, "\\> *\\d{3,4}"))
  opp <- c(opp, str_extract_all(line, "\\d{1,2}\\|"))
}

name <- name[!is.na(name)]
state <- substr(state[!is.na(state)], 2, 3)
points <- points[!is.na(points)]

preR <- regmatches(preR[!is.na(preR)], gregexpr("[[:digit:]]", preR[!is.na(preR)]))
preR <- sapply(preR, paste0, collapse = "")

postR <- regmatches(postR[!is.na(postR)],
                    gregexpr("[[:digit:]]", postR[!is.na(postR)]))
postR <- sapply(postR, paste0, collapse = "")

opp <- opp[seq(1, 192, 3)]
opp <- lapply(opp, gsub, pattern = "\\|", replacement = "")
```

### Data Creation

Create vectors with computed data:

  1. Average Opponent PreRating
  2. I'm so sorry; it's far too late to do the EC problems.... I needed to practice RegEx more than I needed to practice ELO calculation.  I feel ashamed, but also too tired to continue.

```{r}
avgPreR <- c()
for (i in seq_along(name)) {
  total <- 0
  for (opponent in opp[[i]]) {
    id <- as.numeric(opponent)
    total <- total + as.numeric(preR[[id]])
  }
  avgPreR <- c(avgPreR, round(total / length(opp[[i]]), digits = 0))
}
```

### Output the data

```{r}
data <- data.frame(name, state, points, preR, postR, avgPreR)
write.csv(data, "tournament.csv")
```

