---
title: "Working with Web APIs"
author: "Sam Reeves"
date: "4/9/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

### Picking an API

After getting an API key from developer.nytimes.com/apis, I have opted to use the Article Search API.  I want to know about all the NYTimes articles concerning the very center of the universe: Absolute Bagels on the UWS.  When I left NYC, I would sometimes wake up from bagel dreams, chewing on a wet pillow.  Maybe this will help me relive my everything-double-toasted-with-butter days.

```{r}
library(httr)
library(jsonlite)
```

### Building an API call

An API call consists of a few necessary parts, and many optional ones. 
Here's an example:

```
GET https://api.nytimes.com/svc/search/v2/articlesearch.json?q=%22absolute%20bagels%22&sort=relevance&api-key=XXXXXXXX
```

1. the base URL 
2. the query string 
3. "&api-key="
4. the API key

In our example, we sort the results by relevance, denoted by sort=relevance, and we are just taking the default search results page.

We can construct it like this:

```{r}
base <- "https://api.nytimes.com/svc/search/v2/articlesearch.json?q="
query <- "%22absolute%20bagels%22"
sort <- "&sort=relevance"
ak <- "&api-key="
key <- "rFlQcW68K4OTRn8dpDTy6CeWL1qk23jj"

q <- paste0(base, query, sort, ak, key)
```

We use paste0() instead of paste() because we do not need a separator, and it's a tiny bit more efficient.

Let's make the API call and save the content we are served:

```{r}
req <- GET(q)
cont <- content(req, 'text')
json_data <- fromJSON(cont)

articles <- json_data$response$docs
```
Let's check out the abstracts........

```{r}
articles$abstract
```
