---
title: "Week 3 Assignment"
author: "Sam Reeves"
date: "2/17/2021"
output:
  html_document: default
---
### 1. Using the 173 majors listed in fivethirtyeight.com’s College Majors dataset, provide code that identifies the majors that contain either "DATA" or "STATISTICS"

```{r}
library(magrittr)
library(stringr)
url <- "https://raw.githubusercontent.com/fivethirtyeight/data/master/college-majors/majors-list.csv"

data <- data.frame(read.csv(url))

data$Major[which(str_detect(data$Major, "DATA"))]
data$Major[which(str_detect(data$Major, "STATISTICS"))]
```

### 2. Write code that transforms the data below:

[1] "bell pepper"  "bilberry"     "blackberry"   "blood orange"
[5] "blueberry"    "cantaloupe"   "chili pepper" "cloudberry"  
[9] "elderberry"   "lime"         "lychee"       "mulberry"    
[13] "olive"        "salal berry"

Into a format like this:

c("bell pepper", "bilberry", "blackberry", "blood orange", "blueberry", "cantaloupe", "chili pepper", "cloudberry", "elderberry", "lime", "lychee", "mulberry", "olive", "salal berry")

```{r}
x <- '[1] "bell pepper"  "bilberry"     "blackberry"   "blood orange"  
[5] "blueberry"    "cantaloupe"   "chili pepper" "cloudberry"  
[9] "elderberry"   "lime"         "lychee"       "mulberry"    
[13] "olive"        "salal berry"'

y <- str_remove_all(unlist(str_extract_all(x, '"[a-z]*\\s*[a-z]*"')), '\"')
y
```

### 3. Describe, in words, what these expressions will match:

* (.)\1\1
  + Any tripled character.
* "(.)(.)\\2\\1"
  + Any two characters followed by \2\1, all inside of quotes.
* (..)\1
  + Any pair of characters repeated.
* "(.).\\1.\\1"
  + Any two characters followed by \1, any character, and \1 all in quotes.
* "(.)(.)(.).*\\3\\2\\1"
  + Any character followed by any character, followed by any character, followed by any number of random characters, followed by \3\2\1, all in quotes.

### 4. Construct regular expressions to match words that:

* Start and end with the same character
  + \b([a-z])\w*\1\b
* Contain a repeated pair of letters (eg "church" contains "ch" repeated twice.)
  + \b\w*([a-z]{2})\w*\1\w*\b
* Contain one letter repeated in at least three places (eg. "eleven" contains three e's.)
  + \b\w*([a-z])\w*\1\w*\1\w*\b


