---
title: "tidyingAndTransforming"
author: "Sam Reeves"
date: "3/5/2021"
output:
  html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Load libraries and import .csv
```{r message=FALSE}
library(tidyr)
library(dplyr)
dat <- read.csv("https://raw.githubusercontent.com/TheWerefriend/data607/master/week5/numbersense.csv")
```

# Reshape the data

Separate the two airlines, and create another column of totals.  Create a tibble with all the data, and preserve the city names as a column.
```{r}
alaska <- t(dat[1:2, 3:7])
am_west <- t(dat[4:5, 3:7])
totals <- alaska + am_west

flight_info <- cbind(alaska, am_west, totals)
colnames(flight_info) <- c("AL_OT", "AL_D", "AM_OT", "AM_D", "TOT_OT", "TOT_D")
fi <- tibble::rownames_to_column(as.data.frame(flight_info), "cities") %>%
  tibble()
```

# Summarize the data

```{r}
fi %>%
  summarize(total_percentage = (TOT_D / (TOT_OT + TOT_D)),
            AL_percentage = (AL_D / (AL_OT + AL_D)),
            AM_percentage = (AM_D / (AM_OT + AM_D)))
```
# Conclusions

Phoenix has the lowest percentage of delayed flights in comparison with the other cities.  Northern cities have a higher percentage of delays for both airlines.  Alaska has lower delay percentages than AM West for every single city.